---
title: "grp1_project_package-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{project_package-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, message = FALSE, echo = FALSE, error = FALSE}
library(grp1ProjectPackage)
```

# Introduction to grp1ProjectPackage

The goal of grp1ProjectPackage is to provide simplified functions to achieve the goal of data preprocessing for exploratory data analyses. The grp1ProjectPackage makes the following steps quick and easy:

-   Loading data from an html
-   Removing certain columns from a data set
-   Creating a ggplot boxplot
-   Splitting data into training and testing sets

This document introduces you all of the tools mentioned above as well as examples of how to apply them to data frames and use them in different real-world scenarios.

## 1. Load data from an html using `load_data()`
Desciption ... TODO 
```{r load_data, warning = FALSE, error = FALSE, echo = FALSE}
init_data<-load_data("https://7e6cd356-86ad-4874-abc7-3a69bbbc39e6.filesusr.com/ugd/c5a545_c1b17c070c984dfcb14cf1c3bb0b6e67.csv?dn=garments_worker_productivity.csv")
head(init_data)
```

## Data: `mtcars`

For the purpose of demonstration for the rest of the package, we will use a basic data set called `mtcars`. This data set has 11 columns, 32 rows and is documented in `?mtcars`. Note that `mtcars` is a data frame and below is the first 6 rows.

```{r dataset, warning=FALSE, echo = FALSE}
head(mtcars)
data <- mtcars
```


# Demonstration of basic functions in projectPackage

## 2. Dropping columns with `clean_data()`

Often when you work with large data sets, there will be columns that are redundant or not of interest. In that case, you can use our function `clean_data()` to drop those columns. For details on how to use the function, check out `help(clean_data)`.

-   **dropping a single column `mpg` from mtcars**

```{r data_cleaning1, warning = FALSE, error = FALSE}
head(clean_data(data, "mpg"))
```

As you can see above, the column mpg has been dropped from the data frame.

-   **dropping multiple columns from mtcars**

```{r data_cleaning2, warning = FALSE, error = FALSE}
head(clean_data(data, c("mpg","disp","qsec")))
```

Again, columns `mpg`, `disp`, and `qsec` have been dropped.

-   **When an inappropriate column name is inputted, an error will occur.**

For instance, if I accidentally used the wrong column name mpf instead of `mpg`. The function will kindly produce an error.

`clean_data(data, "mpf")` will produce the following message: *"Error in clean_data(data, "mpf") : column names incorrect. Please try again"*


## 3. Creating a boxplot using `create_boxplot()`

Often times visualizations are needed to better understand the raw/modified data. Data visualization helps in the breakdown of complex problems by transforming data into a more understandable format and showing trends and outliers. A good visualization tells a story by reducing noise from data and emphasizing the most important facts. 

For details on how to use the function, check out `help(create_boxplot)`.

```{r plot, warning = FALSE, echo = FALSE,  fig.width = 7, fig.height = 4}
create_boxplot(mtcars, as.factor(data$cyl), mtcars$mpg, "MPG by No. Cylinders", "No. Cylinders", "mpg")
```

## 4. Splitting data into training and testing sets using `train_test_split()`
Desciption ... TODO 
```{r recipe-scale-center, warning = FALSE, error = FALSE}
 train_test_split(mtcars, 0.75, "mpg")
```
